Relating two Abstractions for Formal Array Languages

### 2014-04-11 paper.tex
Explaining the difference between various functions in MoA and Pull arrays

Figure \ref{fig:rosetta} gives a translation between function names
used in MoA and Pull arrays.

\begin{figure}
\begin{center}
\begin{tabular}{|@{}l|l@{}|}
\hline
MoA & Feldspar
\\
\hline
δ & \verb!dim . extent!
\\
ρ & \verb!extent!
\\
ιξⁿ & generalized \verb!enumFromTo!
\\
ψ & generalized \verb!index!
\\
rav & -- flattens to a one-dimensional array
\\
γ & \verb!toIndex!
\\
γ' & \verb!fromIndex!
\\
$s \: \hat{ρ} \: ξ$ & \verb!reshape!
\\
π x & \verb!product!
\\
τ & \verb!size!
\\
++ & ++
\\
ξ₁ f ξ₂ & \verb!zipWith f! ξ₁ ξ₁
\\
σ f ξ & \verb!map f! ξ
\\
ξ f σ & \verb!map f! ξ
\\
$\bigtriangleup$ & \verb!take!
\\
$\bigtriangledown$ & \verb!drop!
\\
$op^{red}$ & \verb!fold op!
\\
Φ & \verb!reverse!
\\
Θ & \verb!rotate!
\\
$\varobslash$ & generalized \verb!transpose!
\\
$f Ω_d ξ$ & -- Apply $f$ along the dimension $d$ of $ξ$
\\
\hline
\end{tabular}
\end{center}
\caption{A correspondence between functions in MoA and Pull arrays}
\label{fig:rosetta}
\end{figure}

\subsection{Example programs}

>>>>

Figure \ref{fig:rosetta} gives a translation between function names
used in MoA and Pull arrays. The intention of this figure is to work
as a rosetta stone, helping to translate from one formalism to the
other.

As can be seen in the figure, not all operations in MoA have a
corresponding function in the Pull array literature. Some of these
functions are missing because Pull arrays do not have a notion
corresponding to ONF in MoA. In particular, the function $rav$ is used
in ONF to decide on the particular layout of the array, and this step
is implicit for Pull arrays. However, $\Omega$ is a good candidate to
transfer to the formalism of Pull arrays.

The difference between ψ in MoA and \verb!index! i Pull arrays is that
ψ can be used with partial indexes, a central notion in MoA. Pull
arrays solve this problem in a more roundabout way, using a notion of
\emph{slices} \cite{keller2010regular}. We leave out the explanation
of slices for reasons of space.

\begin{figure}
\begin{center}
\begin{tabular}{|@{}l|l@{}|}
\hline
MoA & Feldspar
\\
\hline
δ & \verb!dim . extent!
\\
ρ & \verb!extent!
\\
ιξⁿ & \verb!enumFromTo!
\\
ψ & generalized \verb!index!
\\
rav & -- No corresponding function
\\
γ & \verb!toIndex!
\\
γ' & \verb!fromIndex!
\\
$s \: \hat{ρ} \: ξ$ & \verb!reshape!
\\
π x & \verb!product!
\\
τ & \verb!size!
\\
++ & ++
\\
ξ₁ f ξ₂ & \verb!zipWith f! ξ₁ ξ₁
\\
σ f ξ & \verb!map f! ξ
\\
ξ f σ & \verb!map f! ξ
\\
$\bigtriangleup$ & \verb!take!
\\
$\bigtriangledown$ & \verb!drop!
\\
$op^{red}$ & \verb!fold op!
\\
Φ & \verb!reverse!
\\
Θ & \verb!rotate!
\\
$\varobslash$ & generalized \verb!transpose!
\\
$f Ω_d ξ$ & -- No corresponding function
\\
\hline
\end{tabular}
\end{center}
\caption{A correspondence between functions in MoA and Pull arrays}
\label{fig:rosetta}
\end{figure}
